Due to the recent COVID-19 outbreak, at \acrshort{fhict} education has shifted to online. 
From March to June 2020 education has taken place online exclusively. However, since the start of the academic year 2020-2021, education is blended, e.i. students have partially online and face-to-face classes.
While this choice is purely a necessity to ensure the continuation of education in the context of a pandemic, blending instructional materials with online interventions can be a better setting as opposed to fully online or face-to-face mode of instructions, if done well~\cite{blended2020}. 
In that sense, technology it is not just a vital necessity but also an asset. 
\\\\
In addition to already existing technology such as \Gls{canvas} and \Gls{git}, at \acrshort{fhict}, online lessons are offered via \Gls{mteams}. 
An advantage of \Gls{mteams} is that it provides a solution for both synchronous and asynchronous learning. 
Just as a physical classroom has a specific schedule, using this application it is possible to provide live online lessons at a pre-scheduled time. The platform can also be connected to the regular email and schedule services from Outlook, students being one click away from joining the lessons from their calendars. Moreover, lessons can be recorded for students to review at a later time. With almost one year of education offered fully or partly online, many students have mentioned the advantage of recorded lessons to better prepare for assessments (for instance exams).\\\\
A challenge in the online environment is the visual engagement. Unlike face-to-face, in an online lesson it is challenging to sense student engagement or receive feedback about their understanding. Recently, \Gls{mteams} has been releasing features such as "Rise your hand" and "Together mode" which improve the overall communication channel and make the online environment more physical. Furthermore, the Polly extension of \Gls{mteams} to manage voting options is a tool I make use of on a regular basis for polls and opinion gathering. \Cref{appendices:ms_teams} shows some examples of conduction lessons in \Gls{mteams}. 



