\chapter{ALE example personas}\label{appendices:personas}

\subsubsection{Examples personas for \acrfull{ale}}
\subsubsection{Filip}\\\\
Filip is a fourth year ICT \& Technology student which has has just finished his internship and is now in choosing his elective which will be his last courses before the graduation. 
Filip is a highly motivated student which always wants to learn something new and challenge himself. 
Ever since he chose Technology as a main programe, he has dived deeper into the topic and studied in depth processes and technologies in his field of study. 
However, with the internship, he has investigated technology using Data Science, a topic he has never studied in with his regular program.\\\\
Hence, Filip is now looking for courses which are motivating and contribute to his general knowledge  and preparation as a young professional. 
He is especially interested in object-oriented programming, as he as mainly worked in a low level programming of machines and robots and would like to practice the higher level programming.
\subsubsection{Angela}\\\\
As a ICT \& Software student, Angela is in her final programe year, looking to choose elective courses. Angela really enjoys software engineering, and would like to gain as much experience in this field as possible. She is no expert, however, she is willing to improve further. While the electives usually reflect courses from several programs (e.i. Technology, Business), Angela prefers to choose the software courses.\\\\
Angela is especially lacking practice in designing good software architecture from scratch, including UML and unit testing. As she is wishes to become a software engineer, she is looking for courses that help her practice these aspects.
\subsubsection{Tom}\\\\
Tom has finished all his first two years courses and the minor all within the ICT \& Software programe. However, Tom did not manage to find an internship to his liking, namely Game Design. This is a great opportunity for Tom to see if Game Design is really for him and, thus, he  would really like to join such an internship. In order to not waste half a year of his study, Tom requested an alternative to join some fourth year electives instead. As the faculty has allowed his request on the elective course teacher accept, Tom is not searching for elective courses that he can attend.


