Subsequently, the course material development followed. 
While original topics and assignments were preserved, only instructional materials were reworked.
Having rather considerable experience with the course subject, the task of developing lesson material suit me well. 
Furthermore, I have had the experience of fine-tuning instructional materials previously for other courses. The deliverables from this phase were:  
\begin{itemize}
    \item lesson slides
    \item assignment and supportive information (course notes)
    \item practice assignments
    \item \Gls{canvas} master course
\end{itemize}
While I could adapt and reuse former assignment examples, the majority is developed from scratch. 
I also added practice assignments (additional exercises) as a preparation for the assignment. 
Furthermore, example solutions of the assignments were constructed to aid future course teachers and reduce their preparation time.\\\\
A sample presentation along with the corresponding assignment and supportive information is provided in~\cref{appendices:slide_assignment_info}; this appendix includes also a sample solution and corresponding code snippet. 
An example of a \Gls{canvas} page is also attached in~\cref{appendices:slide_assignment_info}.\\\\
The most challenging task was to develop appropriate examples and practice assignments which would provide the basic understanding and would still require further self-engagement from the students.
Furthermore, researching trusted sources for further reading proved to be more time-consuming than expected. 
However, this experience has turned out to be quite enjoyable, and in the future I am looking forward to other development opportunities, even curriculum development.