A student-centered education envisioned by \acrshort{fhict} requires a student-centered assessment~\cite{FHICTAssesmentPolicy}. 
This implies frequent \textit{formative feedback} and \textit{feed forward} for the students throughout their learning process. 
\textit{Formative assessment}, thus, benefits not only the students, but also the lecturer, who can get a better picture of the student and his development during the education by collecting and interpreting information on the student performance.\\\\
While the learning outcomes for the \acrshort{ale} elective defined during the design phase in~\cref{chapter:didactics_phase_design} form the basis of the integral assessment, weekly teacher feedback is aimed to appreciate ongoing development and performance.
For that reason, the assessment consists of smaller components which at the end form an integral assignment.\\\\
From the first iteration of the course, I realised that students were either not attending the formative feedback sessions or not actively working on the course topic due to various reasons. 
This ultimately yield to a rather poor integral assessment. 
Considering this outcome, in the concurrent iteration of the course I made the formative feedback sessions mandatory.
I asked students to submit their weekly progress or shorty describe their reason of delivering up to mark. However, the performance did not significantly change, rather worsen.
In~\cref{appendices:scores} a histogram of the integral assessment scores and the significance difference test score is shown. Another aspect to consider about the course is that it is an elective, thus, students may have various reasons to participate, as shown in the recent course survey in~\cref{appendices:survey}. Throughout the course iterations I also noticed many students usually drop \acrshort{ale} after the first two weeks, as they cannot fit the workload with their rest of the educational path/personal life, although always advised even from the fist lesson (some students are doing their graduation and are looking for opportunities to fill in the last 3\Gls{ec}s or some are free-riders due the format of the course, e.i. no exam). Therefore, the mandatory weekly formative assessment was left out in the end.