While my didactical skills were highly influenced by my former teachers, I recognized opportunities to \textit{improve learning} based on my experience as a \acrshort{fhict} alumna. 
Ever since starting working at Fontys I remodeled course material, developed testing assignments and exams and experimented pedagogical practices, all within the already existing course learning outcomes.\\\\
Commonly, the \acrshort{fhict} English stream curriculum includes course material. 
However, even as a student, I identified a fourth year ICT \& Software Engineering elective, \acrfull{ale}, which significantly lacked course material (see 2017 version course material in~\cref{appendices:course_materials}). 
Having prior knowledge about the subject, taking the role of teacher was natural. 
However, after several iterations and feedback from students (see written feedback from July 2020 students in~\cref{appendices:survey}), I concluded that further course material development is necessary. 
While extensive course material may improve a student's overall learning experience, it could also aid a future course teacher to better understand the subject.\\\\
As \acrshort{fhict} is student-centered, the teacher plays an important role in the assessment process~\cite{FHICTAssesmentPolicy}.
So far, I have taken the role of test developer, reviewer and examiner for software courses, which is my field of expertise. Moreover, while iterating through the fourth year ICT \& Software Engineering elective \acrshort{ale}, I learned that frequent close guidance and feedback and feed forward strategy that I aimed for resembles the \acrshort{fhict} formative assessment educational vision.\\\\
\Acrfull{tel} plays an important role in \acrshort{fhict}. Through various technologies, tasks such as teaching, assessment and feedback are being carried out. 
Lately, \Gls{canvas} has become the learning management system within \acrshort{fhict}, gradually replacing the former prime data source \Gls{sharepoint}. 
I quickly gained experience co-creating and managing \Gls{canvas} courses, especially while iterating through the \acrshort{ale} elective course.\\\\
During the ongoing COVID-19 crisis, the entire teaching has shifted to primarily online. 
However, this event has brought great opportunities to further showcase my \acrshort{tel} skills. 







